### 2024-08-11 doc/Thesis/chapter/01-introduction.tex
start doing todo.md

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g. wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
%
One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple solar cells are connected in series. 
The solar cells must be deposited on a non-conducting surface.
Glass is a popular non-conducting substrate, but rigid and brittle. 
A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g. tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
Sol-gel processes often produce porous layers, though.

>>>>

%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Photovoltaics (PV) is a viable renewable energy source towards energy neutrality.
Furthermore, 
it uses the sun's energy directly in contrast to other energy sources (e.g.\ wind, water or even carbon based) and therefore 
it is fit to be used in energy harvesting projects like futuristic Dyson spheres\cite{dyson1960search, kardashev1964transmission} which harness the whole power output of the sun.
%
One type  of thin film PV is based on the CIGS (copper indium gallium sulfide) semiconductor absorber\cite{Vasekar2010}. 
Due to the large light absorption coefficient of CIGS (compared to silicon), less absorber material is needed (a couple of micrometers) and the PV cell can be made thinner and flexible. 
%\td{was sind vorteile?}
In order to make a module, multiple solar cells are connected in series. 
The solar cells must be deposited on a non-conducting surface.
Glass is a popular non-conducting substrate, but rigid and brittle. 
A flexible alternative is steel foil, which is ductile, inexpensive and highly available, but electrically conducting. 
An insulating layer must therefore be applied to the steel substrate before any CIGS cells can be deposited on top.
Polymers would be a choice if not for their low thermal stability which does not permit high production temperatures.
A non-toxic material which is suitable for the insulation is zirconium oxide (\ch{ZrO2}). 
%An economic and scalable method is doctor blading via a sol-gel process. 
Sol-gel roll-to-roll coating processes (e.g.\ tape casting) are economic and scalable methods to apply liquid precursors to substrates, and have been also reported for the deposition of \ch{ZrO2}\cite{yeo1998design,michalek2015comparison}.
Sol-gel processes often produce porous layers, though.

### 2024-08-11 doc/Thesis/chapter/020-theory-materials.tex
start doing todo.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into electric energy can be broken down into two essential steps: 
the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
%This is often achieved through a p-n junction.
The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g. silicon); if not, heterojunctions (e.g. \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

\begin{figure}[tbh]
	\includegraphics[width=\textwidth]{./Pics/cigs.png}
    \caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell.\cite{rau2013cigs}}
	\label{fig:cigs}
\end{figure}

@@

%
Instead of glass as substrate, steel and polymers (e.g. polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
Thus, an insulating layer has to be deposited on the steel substrate. 
%The conductance of steel can be masked by a insulator layer (e.g. \ch{ZrO2}, \ch{Al2O3}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions, which are accelerated to the surface, mostly originate from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g. argon) in plasma phase are mainly used for bombardment because of their inert properties. 
Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g. \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

@@

%what is sputtering? \\
% Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
%This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
%\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
%Sputtering is of the latter kind, which is advantageous if substrates can't withstand high temperatures.
%\td{what can it be used for?}\\
%Sputtering evolved from being a curious experiment in the middle of the 20th century to 
%having various applications in research and engineering.

@@

\iffalse
A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
This lowers the pressure needed to sustain the plasma. 
Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
undoing the deposited layer.
This also increases the probability of an electron 
colliding with an argon atom and ionizing it, increasing the yield.
%
When oxygen or nitrogen are added to the gas this is called reactive sputtering.
Sputtered atoms will react with the gas and result in oxide or nitride layers, respectively.
The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning;
meaning that the target is being passivated by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}. 
%
The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
This prevents charge from building up on the target. \linebreak[2]
Although radio frequency sputtering is more versatile, directional current sputtering is more common because of it's simpler system and economical reasons.
%\td{sputtered particles are neutral and not influenced by the electrical field}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
\td{FORMATTING: In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the velocity $v=c/n(\lambda)$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:}
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
%\td{it's adsorbed by certain groups?)} 
vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}/\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy of the photon must be the same as the difference between two electronic states. %, a lower populated and a higher empty orbital.}
The electron will then be excited into a energetically higher orbital.
Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Photovoltaics Basics}
The process of conversion of photons into electric energy can be broken down into two essential steps: 
the generation of an electron-hole pair through photon absorption, the electron-hole separation by the built in electric field at the p-n junction and finally collection of the electrons and holes at the opposite terminals of the device\cite{markvart2013principles}.
This means that \gls{pv} cells are basically diodes, which have a low resistance in one direction and a high resistance in the other direction. 
%This is often achieved through a p-n junction.
The n-type side of the p-n junction has excess electrons and p-type side has excess electron holes. 
If the n- and p-type are of the same basis material, they are called homojunctions (e.g.\ silicon); if not, heterojunctions (e.g.\ \ch{CdS}/\gls{cigs} and \ch{CdS/CdTe})\cite{breitenstein2013understanding}.
%
The first marketable \gls{pv} were crystalline silicon photovoltaic modules which still 
have the biggest market share in the \gls{pv} segment (including polycrystalline and monocrystalline silicon).
In 2022 over 88\% of all sold \gls{pv} where made of silicon (including amorphous silicon)\cite{breitenstein2013understanding}.
%
A comprehensive overview on different \gls{pv} technologies can be found in \cite{markvart2013principles}.

@@

\begin{figure}[tbh]
	\includegraphics[width=\textwidth]{./Pics/cigs.png}
    \caption{Schematic layer sequence of a standard \ch{ZnO}/\ch{CdS}/\ch{Cu(In,Ga)Se2} thin-film solar cell\cite{rau2013cigs}.}
	\label{fig:cigs}
\end{figure}

@@

%
Instead of glass as substrate, steel and polymers (e.g.\ polyimide\cite{feurer2017cigs}) can be used to create flexible \gls{cigs} modules. 
They both come with their own inconveniences. 
Polymers generally have low thermal stability compared with ceramics and metals which restrict the fabrication temperature of \gls{cigs}.
Steel, on the other hand, is temperature resistant enough, but is an electric conductor, which is problematic for the serial interconnection of cells into modules. 
Thus, an insulating layer has to be deposited on the steel substrate. 
%The conductance of steel can be masked by a insulator layer (e.g.\ \ch{ZrO2}, \ch{Al2O3}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Contact Deposition by Sputtering}
%SPUTTERING FREEWRITING: 
% what is sputtering?
Sputtering describes the process of highly energetic ions bombarding a surface and atoms being ejected from the surface as a consequence.
% what can it be used for? 
%It can be used for high precision etching (semiconductors and nanomaterial) or to deposit thin films. 
%
Use cases vary from thin films depositions for \gls{pv}, 
for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of sputter-deposited thin films include good adhesion to the substrate 
and good step coverage\cite{Swann1988}.
% how does it work? 
%A plasma is created and the ions are accelerated to the surface. 
The ions, which are accelerated to the surface, mostly originate from a plasma.
The ion bombardment leads to a transfer of momentum from the ions to the surface atoms which in turn leads to a collision cascade. 
The cascade can reach the surface again. 
If the energy of an atom is larger than the binding energy, the atom is ejected. 
%If a surface particle obtains momentum pointing away from the bulk and its kinetic energy is higher than the binding energy, the particle is sputtered. 
This neutral ejected particle travels -- unaffected by the electrical field nearly perpendicular to the surface -- towards the substrate and condenses with other particles to form a layer.
The pressure in the chamber should be small, such that the sputtered particle has a long mean free path, but on the other hand 
a minimum pressure is needed to sustain the plasma.
Usual pressures are around \SI{1}{\Pa} (\num{e-2}\SI{}{\milli\bar}) or lower\cite{Swann1988}.
% what is used? 
Nobel gases (e.g.\ argon) in plasma phase are mainly used for bombardment because of their inert properties. 
Oxygen or nitrogen can be added to the plasma to deposit oxides or nitrides, respectively.
%Reactive gases can be added (e.g.\ \ch{O2} or \ch{N2}).
In order to use sputtering for depositing a target material on top of a substrate material, 
the target and the substrate are positioned parallel and in between the gas is transitioned into plasma and the ions are accelerated in the direction of the target (by a high electrostatic potential).

@@

%what is sputtering? \\
% Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
%This is called a \gls{pvd} technique in contrast to chemical vapor deposition. 
%\Gls{pvd} can be divided into activation by thermal energy and activation by energetic particle bombardment. 
%Sputtering is of the latter kind, which is advantageous if substrates can not withstand high temperatures.
%\td{what can it be used for?}\\
%Sputtering evolved from being a curious experiment in the middle of the 20th century to 
%having various applications in research and engineering.

@@

\iffalse
A magnetron can be placed behind the cathode (target) in order to trap the plasma close to the source. 
This lowers the pressure needed to sustain the plasma. 
Furthermore, magnetrons prevent high energy electrons from reaching the substrate and 
undoing the deposited layer.
This also increases the probability of an electron 
colliding with an argon atom and ionizing it, increasing the yield.
%
When oxygen or nitrogen are added to the gas this is called reactive sputtering.
Sputtered atoms will react with the gas and result in oxide or nitride layers, respectively.
The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning;
meaning that the target is being passivated by an insulating layers which can lead to defects in the growing film\cite{Kelly2000}. 
%
The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
This prevents charge from building up on the target. \linebreak[2]
Although radio frequency sputtering is more versatile, directional current sputtering is more common because of its simpler system and economical reasons.
%\td{sputtered particles are neutral and not influenced by the electrical field}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\subsection{UV/Vis/NIR Spectroscopy}
%%% WHAT? 
\Gls{uv}/\gls{vis}/\gls{nir} spectroscopy is a molecular spectroscopic method using 
interactions of \gls{uv}/\gls{vis}/\gls{nir} light 
(wavelengths of \num{e-7} to \num{e-6}\m{}) with molecules\cite{Schwedt2008}.
\td{FORMATTING: In general, light is described as periodic \gls{em} wave 
which - in vacuum - moves with the speed of light ($c = \mps{299792458}$)\cite{gHobel2006international}.
In other materials light moves with the speed $v=c/n(\lambda)$, where $n(\lambda)$
is the refractive index which is dependent on the wavelength $\lambda$. 
%is the refractive index which is a function of the wavelength $\lambda$. 
The relation of the energy of a photon~$E$, its frequency~$\nu$, wavelength~$\lambda$ and wave number~$\bar{\nu}$ are as follows:}
\begin{align*}
	E &= h \cdot \nu \\
	\nu &= c/ \lambda \\
	\bar{\nu} &= 1/\lambda,
\end{align*}
where $h$ is Planck's constant.
%In words: shorter wavelength (higher frequency) photons are more energetic.
In practice the spectrum of \gls{em} waves is sectioned into different ranges; % (\td{see figure?+table});
from high to low energy: X-ray, \gls{uv}, \gls{vis}, (near, middle and far) \gls{ir}, microwaves and radio waves. 
X-rays interact with core electrons, \gls{uv}/\gls{vis} with valence electrons, \gls{ir} with 
%\td{it is adsorbed by certain groups?)} 
vibrations of certain groups, microwaves with molecular rotations and radio with electron and nuclear spins. 
%
% UVVis
Two prerequisites need to be fulfilled in order for a \gls{uv}/\gls{vis} photon to be 
absorbed by a molecule or atom.
Firstly, the energy of the photon must be the same as the difference between two electronic states. %, a lower populated and a higher empty orbital.}
The electron will then be excited into a energetically higher orbital.
Secondly, the electronic spin state of the molecule has to be the same before and after, otherwise the transition is quantum mechanically "forbidden" and the absorption is extremely unlikely.
